Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-12-09 cover-letter/refactor-letter.tex
Revise the introduction as per reviewer comments
Add new BriefCASE workflow figure
Revise case study with discussion and larger figures

To aid in reviewing this new refactored manuscript, I am including here a detailed summary of the changes, and where possible, the submission itself indicates the changes directly to make it easier for the reviewers to inspect.
\begin{itemize}
  \item We rewrote the abstract to be active present tense, define the problem, approach, contributions, and results.
\end{itemize}

>>>>

To aid in reviewing this new refactored manuscript, I am including here a detailed summary of the changes, and where possible, the submission itself indicates the changes directly to make it easier for the reviewers to inspect.
\begin{itemize}
  \item We rewrote the abstract to be active present tense, define the problem, approach, contributions, and results.
  \item We revised the introduction to pull in the last three paragraphs of section two, and to better funnel readers from the big picture, intuitive overview, to specific details on our tools and contributions. 
  \item We added is discussion section to the case study in section 8 to address lessons learned from our experience. We also enlarged significantly figures 14 and 17.
\end{itemize}

### 2022-12-09 paper/case-study.tex
Revise case study with discussion and larger figures

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{figs/sw-initial.png}
	\caption{Initial software architecture.}
	\label{fig:sw-initial}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\columnwidth]{figs/hardened-sw.png}
	\caption{Cyber-resilient software architecture.}
	\label{fig:hardened-sw}
\end{figure}

@@

% \begin{figure}[h]
% 	\centering
% 	\includegraphics[width=0.8\columnwidth]{figs/mitigation-output.png}
% 	\caption{Cyber-resilient system response.}
% 	\label{fig:mitigation-output}
% \end{figure}

>>>>

\begin{figure*}[h]
	\centering
	\includegraphics[width=2\columnwidth]{figs/sw-initial.png}
	\caption{Initial software architecture.}
	\label{fig:sw-initial}
\end{figure*}

@@

\begin{figure*}[h]
	\centering
	\includegraphics[width=2\columnwidth]{figs/hardened-sw.png}
	\caption{Cyber-resilient software architecture.}
	\label{fig:hardened-sw}
\end{figure*}

@@

\subsection{Discussion}

\newjunk{
The case study demonstrated the viability of writing code contracts and synthesizing implementations from code contracts in a real-world system. It additionally provided insights for improvement.  We discovered very early that we needed a mechanism to test contracts.  We initially used the synthesis path with a custom test harness for the synthesized code, but this proved to be slow and cumbersome because we had to move back and forth between the OSATE environment and an external test platform. Test contracts are a direct result of our experience, and they obviate the back and forth by integrating test into the modeling and analysis environment.
}

\newjunk{
Writing code contracts for the more complex monitors revealed that although the language is very effective at declarative specifications that define what is being calculated, it is non-intuitive, and sometimes cumbersome, for defining how the computation needs to take place. The primary reason for its unease in describing how computation is performed is that it lacks any type of iterative looping structure for arrays. Instead, it relies on folding and mapping to describe such computation which is non-intuitive for many types of array updates. Growing the expressiveness of the language arround arrays is something to investigate in future work.
}

\newjunk{
	There are several, practical, low-level concerns that need to be addressed in the high-level model before synthesis takes place that in our process were only discovered after running the actual system on the designated hardware and software. We specifically found it difficult to know the memory bounds for heaps, stacks, and buffers and time bounds for the scheduler \emph{a priori} to code synthesis. As a result, we would have to employ a costly iterative approach to set bounds, synthesize code, and then check if anything failed. Integrating better memory and running time analysis at the modeling level is something to investigate in future work.  
}
% \begin{figure}[h]
% 	\centering
% 	\includegraphics[width=0.8\columnwidth]{figs/mitigation-output.png}
% 	\caption{Cyber-resilient system response.}
% 	\label{fig:mitigation-output}
% \end{figure}
